Ontario Graduate Scholarship: Plan of Study

### 2020-04-13 latex/ogs/main.tex
Edited some phrasing to get Final v4

Mechanical systems can be constrained in two ways. Holonomic constraints
restrict position (for instance, car tires remain a fixed distance apart), while
nonholonomic constraints restrict velocities (such as how car tires cannot
slide sideways). Previous research has shown that one can enforce holonomic
constraints through a robot's actuators, using the method of "virtual holonomic
constraints" (VHCs) \cite{vhcs_for_el_systems}. VHCs have been used to control
walking robots \cite{stable-walking}, autonomous bicycles \cite{bicycle},
gymnastics robots \cite{xingbo-thesis}, and snake robots \cite{snake-robot}
among others. These VHCs are a special case of the more general virtual
nonholonomic constraints (VNHCs); in my master's thesis \cite{my-thesis} I
developed a theory for enforcing VNHCs and designed one which injects energy
into the gymnastics robot created by Wang \cite{xingbo-thesis}, thereby enabling
it to perform backflips on a bar.

@@

Mohammadi \textit{et.al.} \cite{manfredi-orbit-stabilization} showed that a
single VHC can result in several motion patterns (known as ``orbits"), from
which one specific motion pattern can be chosen if the robot is initialized with a
configuration that is ``close enough" to it. However, their method does not
work for all starting configurations of the robot. We propose to extend this
work by investigating a method for transitioning between VHCs and VNHCs.

VNHCs have been studied with applications to human-robot cooperation
\cite{vnhc-human-robot-coop} and walking robots \cite{vnhc-biped-robot}. Horn
\textit{et.al.} \cite{hybrid_zero_dynamics_bipedal_nhvcs} have also examined
properties of VNHCs for general mechanical systems and applied their results to
stabilizing a chosen gait on walking robots. Our approach is novel since we 
assume one has already stabilized a VNHC, and will develop techniques to
transition to a second one while maintaining certain safety
constraints. Doing so should allow one to start at any configuration and chain
together VNHCs which drive the configuration close enough to a desired orbit for
stabilization.

@@

The advancements in mathematics from this research will bring improvements to
the control of other autonomous systems. The ability to transition between
complex constraints will allow for more natural expressive motion and may become
a standard technique for controlling biologically inspired robots.

>>>>

Mechanical systems can be constrained in two ways. Holonomic constraints
restrict position (for instance, car tires remain a fixed distance apart), while
nonholonomic constraints restrict velocities (such as how car tires cannot
slide sideways). Previous research has shown that one can enforce holonomic
constraints through a robot's actuators, using the method of "virtual holonomic
constraints" (VHCs) \cite{vhcs_for_el_systems}. VHCs have been used to control
walking robots \cite{stable-walking}, autonomous bicycles \cite{bicycle},
gymnastics robots \cite{xingbo-thesis}, and snake robots \cite{snake-robot}
among others. These VHCs are a special case of the more general virtual
nonholonomic constraints (VNHCs). In my master's thesis \cite{my-thesis} I
developed a theory for enforcing VNHCs and designed one which injects energy
into the gymnastics robot created by Wang \cite{xingbo-thesis}, thereby enabling
it to perform backflips on a bar.

@@

Mohammadi \textit{et.al.} \cite{manfredi-orbit-stabilization} showed that a
single VHC can result in several motion patterns (known as ``orbits"), from
which one specific motion pattern can be chosen if the robot is initialized with a
configuration that is ``close enough" to it. However, their method does not
work for all starting configurations of the robot. We propose to extend this
work by investigating a method for transitioning between VNHCs.

VNHCs have been studied with applications to human-robot cooperation
\cite{vnhc-human-robot-coop} and walking robots \cite{vnhc-biped-robot}. Horn
\textit{et.al.} \cite{hybrid_zero_dynamics_bipedal_nhvcs} have also examined
properties of VNHCs for general mechanical systems and applied their results to
stabilizing a chosen gait on walking robots. Our approach is novel since we 
assume one can stabilize two distinct VNHCs independently, and will develop
techniques to transition between them while maintaining safety constraints.
Doing so will allow one to chain together VNHCs which drive a robot's
configuration towards a desired orbit, regardless of the initial configuration.

@@

The advancements in mathematics from this research will bring improvements to
the control of other autonomous systems. The ability to transition between
complex constraints will allow for more expressive motion and may become
a standard technique for controlling biologically inspired robots.
